Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-13 RR_manuscript/Draft_RR.Rmd
♻️ - edit msa sd

```{r load-models, message=FALSE, warning=FALSE}
msa_mean_sd_df <- read_csv("data/analyses/msa_mean_sd_df.csv") %>%
  filter(transformation == "none", mean > 10)

msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

@@

compelling_count_nest <- table(post_meta_nest$compelling)
```

>>>>

```{r load-models, message=FALSE, warning=FALSE}
msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

@@

compelling_count_nest <- table(post_meta_nest$compelling)

# MSA SD ----

msa_mean_sd_df <- read_csv("data/analyses/msa_mean_sd_df.csv") %>%
  filter(transformation == "none", mean > 10, temporal_window != "sentence")

meta_sd_clo <- meta_bm_tidy$conf.low[["sd_model_id__Intercept"]] 
meta_sd_chi <- meta_bm_tidy$conf.high[["sd_model_id__Intercept"]]

msa_sd <- msa_mean_sd_df %>% group_by(outcome, temporal_window) %>%
  summarise(
    sd_min = min(sd),
    sd_med = mean(sd),
    sd_max = max(sd),
    .groups = "drop"
  )

msa_sd_
```
